---
title: "Tips for using Git and GitHub"
author: "Tom Palmer"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    # toc: true
    # toc_float:
    #   collapsed: false
    #   smooth_scroll: false
    # toc_depth: 2
    code_download: true
    code_folding: show
    anchor_sections: true
---

```{r setup, include=FALSE}
# require("Hmisc")
knitr::opts_chunk$set(echo = FALSE)
```

<!-- `r Hmisc::hidingTOC(levels = 2)` -->

## Introduction

The following is intended as a set of tips for people learning how to use Git and GitHub.

## Tips {.tabset .tabset-pills .tabset-fade}

### Git

- Git is commonly referred to as version control software
- It is better described as a content tracking software
- Git was written to allow developers work on the source code of the Linux kernel
- `.git` folder

### Git grammar

- Follow the tidyverse recommendations about commit messages from [here](https://style.tidyverse.org/gitgithub.html)

### Installing Git

- Windows
- macOS comes with an out-dated version of Git, so use the Homebrew version instead by installing Homebrew, see instructions [here](https://brew.sh/), then running in Terminal  
```
brew upgrade
brew install git
```

### GitHub intro

### GitHub PAT for R

- To create a GitHub PAT to be allowed more downloads from GitHub per hour run in R  
```{r, echo=TRUE, eval=FALSE}
install.packages("usethis")
library(usethis)
create_github_token()
```

### GitHub Desktop


### GitHub CLI

- CLI stands for command line interface


### Workflow



